PeerMind

### 2016-08-11 paper.tex
Some questions and answers.

>>>>

\todo[inline]{Main questions and answers follows.}

What problem are we solving? Why is it important to solve?

Finding a way to lower attention required but increase legitimacy of democratic decisions.
Traditionally legitimacy is increased by increasing participation/attention required.
It is an everlasting problem.
How to outsource governance and at the same time assure it does not get corrupt
or tyrannic.

Has anyone else tried to solve it or related problems? How did they try
and what were the results (subjective or objective)?

Described here: \url{http://mitar.tnode.com/post/73983101095/peer-to-peer-voting-scheme}.
Some tried delegations, but mostly only to one person.
Getting issues that you have tree-structure with possible cycles you cannot resolve.
Often there were reported UI problems as well.
So just technically improving is not enough, you also have to have UI for the technical solution so that people can trust.

How are you solving the problem?
Using dynamic quorum, score voting, delegation, and nice integration with UI/UX.

How will you know how well you solved the problem?
If it improves decision making, participation, inclusivity, activity of people engaged in decision making in my house.
So currently we have issues with reaching the quorum and many people do not participate.
I would like for them to have easier time participating (less time required) and as a consequence more people to
participate collectively.
If I observe that I think I will know I solved the problem.
